---
title: "python"
author: "imabr777"
date: "February 18, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Part 3 - Conditionals
## Task 10

```{r, echo=TRUE}
rand_num <- sample(1:100, size = 1)
rand_num
if (rand_num <= 25){
    print("1st Quartile")
} else if (25 < rand_num & rand_num <= 50){
    print("2nd Quartile")
} else if (50 < rand_num & rand_num <= 75){
    print("3rd Quartile")
} else if (75 < rand_num & rand_num <= 100){
    print("4th Quartile")
}
```

# Part 4 - for loops
## Task 11
```{r, echo=TRUE}
cities <- list("Chicago, IL", "Indianapolis, IN", "Columbus, OH", "Detroit, MI", "Milwaukee, WI", "Kansas City, MI")
for (city in cities) {
  print(paste("Warning, residents of ", city, ", temperatures will reach sub-zero temperatures today, please stay indoors if possible", sep=""))
}
```

## Task 12
```{r, echo=TRUE}
states <- list("Washington","California","Nevada","Idaho","Montana","Utah","Colorado","New Mexico")
result_list <- list()
for (state in states) {
  temp <- paste("U://Users/Im/Geog_458/", state, ".shp", sep="")
  result_list <- c(result_list,temp)
  print(temp)
}
result_list
```

## Task 13
```{r, echo=TRUE}
i = 10
while (i >= 0) {
  print(paste("T-minus",i))
  i = i - 1
}
```

# Part 5 - Functions
## Task 14
```{r, echo=TRUE}
countdown <- function(start) {
  while (start >= 0) {
    print(paste("T-minus",start))
    start = start - 1
  }
}
countdown(17)
```

## Task 15
```{r, echo=TRUE}
quartile_calc <- function(num) {
  if (0 <= num & num <= 25){
    print("1st Quartile")
  } else if (25 < num & num <= 50){
    print("2nd Quartile")
  } else if (50 < num & num <= 75){
    print("3rd Quartile")
  } else if (75 < num & num <= 100){
    print("4th Quartile")
  } else {
    print("Error")
  }
}
quartile_calc(5)
quartile_calc(35)
quartile_calc(55)
quartile_calc(85)
quartile_calc(-5)
quartile_calc(105)
quartile_calc(0)
quartile_calc(100)